Downstream analyses of whole-genome bisulfite-sequencing data

### 2014-12-10 Rmarkdown/appendix.Rmd
Updated appendix

\section{Equivalence of tests to identify DMCs in a one-group experiment}\label{app:one_group_equivalence}

\subsection{Mathematical equivalence}

@@

\subsection{Computational equiavelence}

@@

# Fitting a generalised linear model with a binomial link using two different
# formulations
# (1) Using the array of frequencies
glm(x ~ 1, family = binomial)
# (2) Using relative frequencies (i.e., the beta-values) and weights (i.e.,
  # the sequencing coverage).
  glm(x[,1] / (x[, 1] + x[, 2]) ~ 1, family = binomial, weights = x[, 1] + x[, 2])
```

\section{The probability that two dependent Bernoulli random variables are identical}\label{app:bernoulli_equal}

@@

\section{Estimate of number of CpGs used by \citet{Lacey:2013iy}}\label{app:lacey}

@@

```{r}
devtools::session_info()
```

### TODOs

* Cite data source and publication

>>>>

\section{Chapter \ref{chap:wgbs_downstream_analyses}}

\subsection{Equivalence of tests to identify DMCs in a one-group experiment}\label{app:one_group_equivalence}

\subsubsection{Mathematical equivalence}

@@

\subsubsection{Computational equiavelence}

@@

# Fitting a generalised linear model with a binomial link using two different
# formulations
# (1) Using the array of frequencies
glm(x ~ 1, family = binomial)
# (2) Using relative frequencies (i.e., the beta-values) and weights (i.e.,
  # the sequencing coverage).
  glm(x[,1] / (x[, 1] + x[, 2]) ~ 1, family = binomial, weights = x[, 1] + x[, 2])
```
\section{Chapter \ref{chap:co-methylation_review}}\label{app:co-methylation_review}

\subsection{The probability that two dependent Bernoulli random variables are identical}\label{app:bernoulli_equal}

@@

\subection{Estimate of number of CpGs used by \citet{Lacey:2013iy}}\label{app:lacey}

@@

__TODO__

- R version
- `MethylationTuples`
- `methsim`
- `methtuples`
- others

### 2014-12-10 Rmarkdown/wgbs_downstream_analyses.Rmd
Typos and latex errors
Updated appendix

\chapter{Downstream analyses of whole-genome bisulfite-sequencing data}

@@

We could analyse this table using a simple stand-alone test, such as Pearson's $\chi^{2}$ test. Alternatively, we could frame this as a generalised linear model, either a log-linear model or a logistic regression. The equivalence of these methods is shown in the Appendix.

@@

Regardless of where you draw the line as to what constituted an epiallele, it has become clear that the occurrence of multiple methylation patterns at an m-tuple is the norm rather than the exception when performing bisulfite-sequencing. For example, __FIGURE__ shows the number of methylation patterns observed at 4-tuples with a frequency greater than __WHAT__ from the __WHICH__ sample. There has been some progress in developing software to extract and analyse these epialleles, which I now describe.

>>>>

\chapter{Downstream analyses of whole-genome bisulfite-sequencing data}\label{chap:wgbs_downstream_analyses}

@@

We could analyse this table using a simple stand-alone test, such as Pearson's $\chi^{2}$ test. Alternatively, we could frame this as a generalised linear model, either a log-linear model or a logistic regression. The equivalence of these methods is shown in Appendex \ref{app:one_group_equivalence}.

@@

Regardless of where you draw the line as to what constituted an epiallele, it has become clear that the occurrence of multiple methylation patterns at an m-tuple is the norm rather than the exception when performing bisulfite-sequencing. For example, __FIGURE__ shows the number of methylation patterns observed at 4-tuples with a frequency greater than __WHAT__ from the __WHICH__ sample. There has been some progress in developing software to extract and analyse these epialleles, which I now describe. (Alternatively, cite Landan et al.)
